Reformulating phylogenetic mixed models to improve flexibility and speed

### 2019-09-05 phyloglmm_ms.tex
pushing JD's comments

>>>>

\section*{JD's Comments}

Sharpen opening framing somehow. Clarify the basic idea of
taxonomic-based investigations. Intro could have two or three
paragraphs, and could start by explaining either PCM or phylogenetic
regression.

Work on topic sentences. For example, the first paragraph
in the Challenges section has absolutely the wrong topic sentence.
Think of a paragraph as a unit of your story: you need more paragraphs
in many places. This can be achieved with paragraph breaks and some
sentence-shuffling.

I frankly think you could make a lot of progress if you look at every
section and ask: what are my paragraphs, and what should be their
topic sentences?

Clarify the hierarchical structure of the document. It's not
completely clear whether or not challenges is nested under
introduction or is the same level.

In either case, some of the stuff in challenges should be postponed to
methods. Everything pre methods should be aimed at getting across a
high-level message of what this paper is adding.

Challenges needs to be less detailed, and more clear about the
fundamental relationship between methods. You say your method is not
mathematically equivalent the other methods, which sort of implies
that they're all mathematically equivalent to each other. But this
last fact will come as a surprise or even a confusion to the reader.

You should develop a clear point of view on the relationship between
PCM and phylogenetic regression. Sometimes it seems like the former is
broader than the ladder, and sometimes you seem to use them as
synonyms. It kind of seems to me like you could  talk much less about
PCM, I guess this is mostly a paper about phylogenetic regression. Or
maybe it's a paper about "phylogenetic linear models", and we should
just introduce this term?
It kind of seems like methods needs an introductory paragraph before
you jump into the details. I don't usually do that, but this is a
pretty complicated method section.

You need to say how the glmm approach relates conceptually to the
simple phylogenetic regression above it.

Be consistent about your transpose notation.

The text around (3) is quite deep. It is not clear to me what you mean
by term-wise. You have not explained what you mean by grouping
factors.And the J Matrix, which apparently doesn't even need to be
square, is just an identity Matrix. There's probably a way to present
this that would lead to better intuition.

Can you say a little more about the intuition or mechanism behind
Khatri-Rao? KR seems to work on partitioned matrices, but I don't
see clearly how these matrices are partitioned.

The text around (5) should have less words and strive to be more
explanatory. You can rely more on the equation.

Be consistent with the exposition of simulation models. Groups are not
well explained, and you suddenly talk under multi-group about one
observation per species -- presumably that was true for the previous
model?

(6) is too clunky. Is there a way to simplify the notation for MVNs?
Or just for the expandend covariance matrices, I guess.

Platforms is a single huge ¶ where the topic s. is actually tangential
(could literally be removed). See if you can get clear ideas across
and rely more on the table.

"We simulated 100 phylogenetic trees … to simulate responses …" Does
anything after the first ellipsis carry information? What are the
cites supporting?

"Correlation $\rho$ is used in place of covariances" -- what does this mean?

"Each realization was fitted to all model variants using a range of
different platforms." Unnecessarily vague, tighten up here.

Be careful with the word "identical". If pez is really identical, can
you explain briefly why and maybe say "and therefore is not shown"? Is
that why pez doesn't appear in F2?

It should be more clear to the reader when you are using your method
and when you are using older methods. Is F2 all implementations of the
new method? Say so.

F3. What is meant by layout of the packages?

brms coverage is very high in F4. Are you using the right Bayesian method?

In F2 maybe use dashed boxplots for the first two and explain why.
Also, refer to the last three in the same order in the caption as the
legend.

I finally see from T2 that pez and phyr apparently "can't" do the
single group. This should be briefly explained somewhere salient in
text.

F5 and 6 captions are switched. Also, they shouldn't both refer to F2.
Not clear that the speed one should refer to anything, since nothing
obvious seems to be explained about the speed (nor necessarily
needed).

F6. Why is pez fuzzed out? Does this relate to my identicality questions?

F7. This "annotations" thing is actually getting annoying. Are the
captions just unfinished?

Yeah, I'm a stop now. You can take these comments for what they're
worth, but I don't want to see this Chapter again until you've done
all of the macro-editing of the Results section (figures in the right
order, an attempt at captions, figure references correct).
